\documentclass{article} % For LaTeX2e
\usepackage{nips15submit_e,times}
\usepackage{hyperref}
\usepackage{url}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09


\title{CS522 Project Proposal - Predict Grant Application}


\author{
Priyaranjan Behera\\
Computer Science Department\\
North Carolina State University\\
\texttt{pbehera@ncsu.edu} \\
\And
Sai Sri Harsha Kunapareddy\\
Computer Science Department\\
North Carolina State University\\
\texttt{skunapa@ncsu.edu} \\
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\nipsfinalcopy % Uncomment for camera-ready version

\begin{document}


\maketitle


\section{Project description}

This project involves the prediction of the outcome of grant applications in a university. The project will be to incorporate most of the methodologies that has been covered in the class including data preprocessing, feature selection, data transformation and implementaion \& evaluation of different classifiers. 

\section{Dataset}

The dataset is obtained from a Kaggle competition hosted by the University of Melbourne.
\begin{itemize}
	\item 249 multivariate, time-series attributes
	\item 8K data objects
\end{itemize}

\section{Software requirements}

The data processing and classifications will be done in Matlab with extensive use of the Statistics and Machine Learning Toolbox.

\section{Papers to be referred}

\begin{itemize}
	\item Top 10 algorithms in data mining. Knowl. Inf. Syst. 14, 1 (December 2007), 1-37. DOI=http://dx.doi.org/10.1007/s10115-007-0114-2
	\item 8K data objects
\end{itemize}


\section{Work division}

Priyaranjan Behera and Sai Sri Harsha Kunapareddy will work together in this project and most of the work will be done collaboratively. The number of attributes to be processed, preprocessing methodologies and classifier implementations will be split evenly. 

\section{Midterm milestone}

By November 12, we aim to complete the preprocessing steps of the data and start with the classification implementations (Viz. - Decision tree, SVC, Naive-Bayes, Neural Network) 


asd

asd

asd

asd

asd

\end{document}
